### 2021-04-09 manuscript.rmd
extract bib file
add extract_bib: to extract bib entries from the master bib file
small edits

bibliography      : ["/home/chainsawriot/dev/dotfiles/bib.bib"]

@@

Comparative content analysis is a frequently used research design in journalism studies. Comparative content analysis is used in modeling journalistic culture [e.g. @esser:2013:C], comparative news value research [e.g. @burggraaff:2017:T;@wilke:2012], news flow research [e.g. @wu:2000:SDI], among others. A comparative content analysis includes news articles from various outlets and usually also from various countries. Then the included news articles are coded either manually or automatically. Although some comparative content analysis studies are purely descriptive, most of these studies are aimed to study how contextual conditions such as characteristics of media outlets (e.g. political orientation, online versus offline) and their countries (e.g. post-communist country) influence the content of news articles. For example, some hypotheses are "the coverage of foreign countries by the news is primarily  determined  by  geographical  proximity  and  the  status  of  the  covered  country" [@wilke:2012, p.306] and "the  degree  of  opinion-orientation  will  be  highest  in  newspapers  from  Polarized  Mediterranean systems and lowest in those from Anglo-American systems." [@esser:2013:C] Employing the language from epidemiology [@susser:1994], the effect on media content in these hypotheses is assumed to be ecological. It assumes a macro contextual factor (e.g. newspapers from Polarized Mediterranean systems) is associated with an outcome at the micro-level (e.g. degree of opinion-orientation), namely, the article-level.

This study of ecological effect on individual behaviours has a long tradition in social sciences. A famous example was Émile Durkheim’s investigation on the ecological factors associated with suicide. Durkheim found the higher suicide rate among citizens from Scandinvian countries than those from other European countries. Using today’s standard, Durkheim’s analysis is descriptive and this descriptive approach for studying ecological effect is indeed still useful for hypothesis generation in comparative content analysis. An example of hypothesis-generating comparative content analysis is @chan2020combining, in which the sentiment profiles of terrorism coverage from Muslim- and Christian-majority countries were visualized. Hypothesis-generating comparative content analysis, however, is rare. Most studies have a confirmatory outlook. As we see from the example hypotheses above, most of these studies propose hypotheses to test for ecological effects. Traditional (frequentist) hypothesis testing approaches were used: @esser:2013:C lumped multiple outlets from the same country together and then used univariate analysis of variance to test for the differences in the proportion of opinion-orienting articles across countries. In @wu:2000:SDI, multiple stepwise regression was used. These approaches violate the underlying assumptions of the statistical analyses. It highlights the fact that comparative content analysis introduces a feature that researchers usually overlook: media contents are clustered in multilevel. A news article is nested within its media outlet and its media outlet is in turn nested within its country. Such data structure brings two problems: non-atomicity and non-stochasticity.

@@

Using this aggregation method, the unit of analysis effectively switches from article to country. This method is useful when $x$ is the only independent variable, akin @esser:2013:C. It is not technically committing atomistic fallacy, when one uses the value of slope as the evidence for an ecological effect. This method still has important drawbacks. First, it cannot be used for data with more than two levels. In @esser:2013:C, for example, multiple media outlets from the same country were lumped together and in effect, assumed to be homogenous and the information about media outlets was discarded. Second, this method discards a massive amount of information. It is better for analysis of a dependent micro-level variable with a reasonably aggregation function (e.g. counting a binary variable). For numerical variables, aggregation functions such as taking a mean or median cannot capture the spread of the micro-level variable [@bryk:1988:H]. Also, the effective sample size is reduced from the number of articles ($m$) to the number of countries ($n$). Nonetheless, this aggregation method, although inflexible, is still useful when the number of groups (e.g. $n$) is large. It is also useful to collapse micro-levels (e.g. article-level) that are not useful in answering one’s research questions.

@@

What is the probability for this paper being accepted by *Digital Journalism*? Under the frequentist framework (and if *Digital Journalism* were accepting papers stochastically), we can only find this out by repeatedly submitting this paper to *Digital Journalism*, say for 100 times, and then count the frequency of acceptance in these repeated submissions. It is indeed impractical as well as inhumane to the editorial team of *Digital Journalism*. Instead, we assert before submission that this paper has a probability of 24% for being accepted. That is the published acceptance rate from *Digital Journalism*’s website. After this paper is submitted and is not desk rejected, the probability might be around 24 to 30%. After a month of waiting and our confidence is shaken a little, the probability might decrease to 10% to 20%. After the paper is favorably reviewed by two reviewers and an R&R is invited, the probability might increase to 40 to 60%. If you see this paper under the "Latest articles" section of *Digital Journalism*'s website, then the probability is beyond doubt 100% (or 0% if we submit this paper again).

@@

Part 3 (Prior) is arguably the most controversial part of Bayesian analysis. In the *Digital Journalism* example, we can select a reasonable prior (or **informative** prior) of 24% from published information. More often than not, we do not have any information to set an informative prior (e.g. What about *Journal of Communication*?). One option is to consult experts or to make an educated guess. But one person's expert opinion could be another person's wishful thinking. And this perceived subjectivity of specifying prior attracts wide-spread criticism from both statisticians [e.g. @efron1986isn] and social scientists [@elff:2020:MAF;@bryan:2015:MMC].

Undoubtedly, setting prior is consequential to the analysis [@van:2006:PB]. But the influence from prior is greatly weakened, when the data is getting bigger. Also, one can select a weakly informative prior [@lemoine:2019:M] which only specifies the possible range of the posterior [^4]. Some so-called "default weakly informative priors", e.g. $\mathcal{t}(1, 0, 0.25)$, have been suggested for typical regression models [@gelman:2008]. The documentation of Stan also provides information on how to choose a appropriate prior (https://github.com/stan-dev/stan/wiki/Prior-Choice-Recommendations).

>>>>

bibliography      : ["manuscript.rmd"]

@@

Comparative content analysis is a frequently used research design in journalism studies. Comparative content analysis is used in modeling journalistic culture [e.g. @esser:2013:C], comparative news value research [e.g. @burggraaff:2017:T;@wilke:2012], news flow research [e.g. @wu:2000:SDI], among others. A typical comparative content analysis in journalism research includes news articles from various outlets and usually also from various countries. Then the included news articles are coded either manually or automatically. Although some comparative content analysis studies are purely descriptive, most of these studies are aimed to study how contextual conditions such as characteristics of media outlets (e.g. political orientation, online versus offline) and their countries (e.g. post-communist country) influence the content of news articles. For example, some hypotheses are "the coverage of foreign countries by the news is primarily  determined  by  geographical  proximity  and  the  status  of  the  covered  country" [@wilke:2012, p.306] and "the  degree  of  opinion-orientation  will  be  highest  in  newspapers  from  Polarized  Mediterranean systems and lowest in those from Anglo-American systems." [@esser:2013:C] Employing the language from epidemiology [@susser:1994], the effect on media content in these hypotheses is assumed to be ecological. It assumes a macro contextual factor (e.g. newspapers from Polarized Mediterranean systems) is associated with an outcome at the micro-level (e.g. degree of opinion-orientation), namely, the article-level.

This study of ecological effect on individual behaviours has a long tradition in social sciences. A famous example was Émile Durkheim’s investigation on the ecological factors associated with suicide. Durkheim found the higher suicide rate among citizens from Scandinvian countries than those from other European countries. Using today’s standard, Durkheim’s analysis is descriptive and this descriptive approach for studying ecological effect is indeed still useful for hypothesis generation in comparative content analysis. An example of hypothesis-generating comparative content analysis is @chan2020combining, in which the sentiment profiles of terrorism coverage from Muslim- and Christian-majority countries were visualized. Hypothesis-generating comparative content analysis, however, is rare. Most studies have a confirmatory outlook. As we see from the example hypotheses above, most of these studies propose hypotheses to test for ecological effects. In this context usually traditional (frequentist) hypothesis testing approaches were used: @esser:2013:C lumped multiple outlets from the same country together and then used univariate analysis of variance to test for the differences in the proportion of opinion-orienting articles across countries. In @wu:2000:SDI, multiple stepwise regression was used. These approaches violate the underlying assumptions of the statistical analyses. It highlights the fact that comparative content analysis introduces a feature that researchers usually overlook: media contents are clustered in multilevel. A news article is nested within its media outlet and its media outlet is in turn nested within its country. Theoretically with a large enough sample it can be argued that a news article is nested within authors. Such data structure brings two problems: non-atomicity and non-stochasticity.

@@

Using this aggregation method, the unit of analysis effectively switches from article to country. This method is useful when $x$ is the only independent variable, akin @esser:2013:C. It is not technically committing atomistic fallacy, when one uses the value of slope as the evidence for an ecological effect. However, this method still has important drawbacks. First, it cannot be used for data with more than two levels. In @esser:2013:C, for example, multiple media outlets from the same country were lumped together and in effect, assumed to be homogenous and the information about media outlets was discarded. Second, this method discards a massive amount of information. It is better for analysis of a dependent micro-level variable with a reasonably aggregation function (e.g. counting a binary variable). For numerical variables, aggregation functions such as taking a mean or median cannot capture the spread of the micro-level variable [@bryk:1988:H]. Also, the effective sample size is reduced from the number of articles ($m$) to the number of countries ($n$). Nonetheless, this aggregation method, although inflexible, is still useful when the number of groups (e.g. $n$) is large. It is also useful to collapse micro-levels (e.g. article-level) that are not useful in answering one’s research questions.

@@

What is the probability for this paper being accepted by *Digital Journalism*? Under the frequentist framework (and if *Digital Journalism* were accepting papers stochastically), we can only find this out by repeatedly submitting this paper to *Digital Journalism*, say for 100 times, and then count the frequency of acceptance in these repeated submissions. It is indeed impractical as well as inhumane to the editorial team of *Digital Journalism*. Instead, we assert before submission that this paper has a probability of 24% for being accepted. That is the published acceptance rate from *Digital Journalism*’s website. After this paper is submitted and is not desk rejected, the probability might be around 24% to 30%. After a month of waiting and our confidence is shaken a little, the probability might decrease to 10% to 20%. After the paper is favorably reviewed by two reviewers and an R&R is invited, the probability might increase to 40% to 60%. If you see this paper under the "Latest articles" section of *Digital Journalism*'s website, then the probability is beyond doubt 100% (or 0% if we submit this paper again).

@@

Part 3 (Prior) is arguably the most controversial part of Bayesian analysis. In the *Digital Journalism* example, we can select a reasonable prior (or **informative** prior) of 24% from published information. More often than not, we do not have any information to set an informative prior (e.g. What about *Journal of Communication*?). One option is to consult experts or to make an educated guess. But one person's expert opinion could be another person's wishful thinking. And this perceived subjectivity of specifying priors attracts wide-spread criticism from both statisticians [e.g. @efron1986isn] and social scientists [@elff:2020:MAF;@bryan:2015:MMC].

Undoubtedly, setting prior is consequential to the analysis [@van:2006:PB]. But the influence from prior is greatly weakened, when the data is getting bigger. Also, one can select a weakly informative prior [@lemoine:2019:M] which only specifies the possible range of the posterior [^4]. Some so-called "default weakly informative priors", e.g. $\mathcal{t}(1, 0, 0.25)$, have been suggested for typical regression models [@gelman:2008]. The documentation of Stan also provides information on how to choose an appropriate prior (https://github.com/stan-dev/stan/wiki/Prior-Choice-Recommendations).
